Measurement of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross Sections using a DD Neutron Generator for Medical Isotope Studies

### 2018-04-16 First_np_Paper/np_abstract_text.tex
Belatedly added the final journal edits to my local draft.

Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator (HFNG).
The HFNG is a compact neutron generator designed as a \enquote{flux-trap} that maximizes the probability that a neutron will interact with a sample loaded into a specific, central location.  
The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
The cross sections were measured in ratio to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions on co-irradiated indium samples.
Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section for 2.76$^{+0.01}_{-0.02}$ MeV neutrons is reported as    49.3 $\pm$ 2.6 mb (relative to \ce{^{113}In}) or 46.4 $\pm$ 1.7 mb (relative to \ce{^{115}In}), and the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section is reported as 26.26 $\pm$  0.82 mb.
The measured cross sections  are found to be  in good agreement with existing measured values but with lower uncertainty (\textless 5\%), and also in agreement with  theoretical values.
This work highlights the utility of compact, flux-trap DD-based neutron sources for nuclear data measurements and potentially the production of radionuclides for medical applications.

>>>>

Cross sections for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} and \ce{^{64}Zn}(n,p)\ce{^{64}Cu} reactions have been measured for quasi-monoenergetic DD neutrons produced by the UC Berkeley High Flux Neutron Generator (HFNG).
The HFNG is a compact neutron generator designed as a \enquote{flux-trap} that maximizes the probability that a neutron will interact with a sample loaded into a specific, central location.  
The study was motivated by interest in the production of \ce{^{47}Sc} and \ce{^{64}Cu} as emerging medical isotopes.
The cross sections were measured in ratio to the \ce{^{113}In}(n,n')\ce{^{113m}In} and \ce{^{115}In}(n,n')\ce{^{115m}In} inelastic scattering reactions on co-irradiated indium samples.
Post-irradiation counting using an HPGe and LEPS detectors allowed for cross section determination to within 5\% uncertainty.
The \ce{^{64}Zn}(n,p)\ce{^{64}Cu} cross section for 2.76$^{+0.01}_{-0.02}$ MeV neutrons is reported as    49.3\,$\pm$\,2.6 mb (relative to \ce{^{113}In}) or 46.4\,$\pm$\,1.7 mb (relative to \ce{^{115}In}), and the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} cross section is reported as 26.26\,$\pm$\, 0.82 mb.
The measured cross sections  are found to be  in good agreement with existing measured values but with lower uncertainty (\textless 5\%), and also in agreement with  theoretical values.
This work highlights the utility of compact, flux-trap DD-based neutron sources for nuclear data measurements and potentially the production of radionuclides for medical applications.
